\section{The Board Game Committee}

\begin{enumerate}
    \item At the discretion of the Wyvern community meeting, a Board Game committee may be erected.

    \item The objective of the Board Game committee is to organize and host Board gaming events.
    
    \item The Board Game committee consists of at least three members: a \textit{Game Master}, and a \textit{Commissioner of Activities}, and a \textit{Administration Team Deputy}.

    \begin{item}
        The responsibilities and duties of the Game Master of the Board Game committee are:
        \begin{enumerate}
            \item to plan and reserve a space for Board Game committee meetings;
            \item to facilitate Board Game committee meetings;
            \item to seek for and appoint a suitable commissioner of activities for the Board Game committee;
            \item to guide and oversee all financial aspects of the Board Game committee;
            \item to lead the Board Game registration process;
            \item to inform the Wyvern community on the status of the event.
        \end{enumerate}
    \end{item}
    
    \begin{item}
        The responsibilities and duties of the Commissioner of Activities of the Board Game committee are:
        \begin{enumerate}
            \item to set a suitable date and location for the Board Game vent;
            \item to purchase and prepare sufficient provisions for the Board Game event;
        \end{enumerate}
    \end{item}

    \begin{item}
        The responsibilities of the Administration Team Deputy of the Board Game committee are:
        \begin{enumerate}
            \item to facilitate communication between the Board Game committee and the administration team;
            \item to report the progress of the Board Game committee to the administration team;
            \item to discuss the budget and settlement of the Board Game committee with the administration team and to communicate its ratification when consensus has been reached;
            \item to otherwise aid in the organization of the Board Game event.
        \end{enumerate}
    \end{item}

	\item The Game Master may also take the role of Commissioner of Activities upon him. In this case there are only 2 committee members.

    \item The administration team independently appoints, suspends, and discharges the Administration Team Deputy.

    \begin{item}
		\label{item:fee}The Board Game committee may charge a additional fee of max \euro2,- for all attendees.
		\begin{enumerate}
				\item This fee must go in to the Board Games committee's funds.
				\item The fee can be used to buy new board games.
				\item Wyvern Members can vote on the next Board Game that is bought through polls.
				\item When there are sufficient funds the Game Master can buy the game with the most votes, this must be communicated to the board.
		\end{enumerate}
    \end{item}

    \item The Board Game committee may charge non-Wyvern attendees on top of the fee in item \ref{item:fee} an additional premium of max \euro1,- for attending the event. The Board Game committee must properly inform attendees of this premium.

    \item The Commissioner of Activities may exclude certain non-Wyvern members for attending the event before the event has commenced.
    
    \begin{item} If a attendee causes significant disarray or damage of property, the Board Game committee may, in consensus, impose certain sanctions upon that member:
        \begin{enumerate}
            \item expulsion from the grounds; or
            \item charging an additional fee for incurred costs.
        \end{enumerate}
    \end{item}
    
    \item If a attendee causes significant disarray or damage of property, the Board Game committee may, in consensus, request the Wyvern community to exclude said attendee from future events. In such a case, a vote must be held to decide upon the matter.

\end{enumerate}
